Concave reduction in Self-Healing Swarms

### 2018-12-12 paper.tex

\documentclass{ieeeaccess}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
%\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{relsize}
\usepackage{algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\usepackage{array}
%\usepackage{caption}
%\usepackage[caption=false,font=footnotesize]{subfig}
%\usepackage{fixltx2e}
\usepackage{float}
\usepackage{url}
%\usepackage{becs}
\usepackage{listings}
\lstset{%
  basicstyle=\normalsize,
  numbers=left,
  numberstyle=\normalsize,
  stepnumber=1,
  xleftmargin=2em
}
%\usepackage{color}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
%\let\latexvec=\vec
%\let\vec=\latexvec
\interdisplaylinepenalty=2500
\newtheorem{definition}{Definition}
\newtheorem{exampleb}{Example}
\newcommand{\subsubsubsection}[1]{\medskip\par\textit{#1:}}
\newcommand{\card}[1]{\vert{#1}\vert}
\newcommand{\magn}[1]{\vert{#1}\vert}
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{xcolor}
\usepackage{standalone}

@@

\Figure[t!](topskip=0pt, botskip=0pt,
midskip=0pt){figures/stableswarm}
{Agent field effects.\label{methods:FieldEffects}}
%\begin{figure}
%\begin{tikzpicture}
%	\node at (0,0) [circle,fill=black!50]{};
%\end{tikzpicture}
%	\includegraphics{figures/stableswarm}
%\end{figure}

@@

\begin{equation}
\mathcal N_b = \{ (r,\beta) \ldots \}
\label{set:Nb}
\end{equation}
These range and bearing pairs are the relative position vector for each
neighbour $b'$ with respect to the sensor reference frame of agent $b$.
Alternative notations are given in equation \ref{notation}
\begin{equation}
	\mathcal N_b = \{(r,\beta) \ldots \} = \{ (r_{b'}, \beta_{b'}) \ldots \} = \{
	\vec{b'} \ldots \}
	\label{notation}
\end{equation}

The model use is the same as that defined by Eliot et. al. in their paper that introduces a new magnitude based metric~\cite{EKB:18}. 
Equation~\ref{eq:BotPhysics1} defines a weighted model that includes cohesion,
repulsion, direction and obstacle avoidance ($\vec v_c(b), \vec v_r(b),
\vec v_d(b), \vec v_o(b)$). 
The weightings $k_c, k_r, k_d, k_o$ allow each component to be scaled to tailor the swarming effect.

\begin{equation}\label{eq:BotPhysics1}
  \vec v(b) = k_c\vec v_c(b) + k_r\vec v_r(b) + k_d\vec v_d(b) + k_o\vec v_o(b)
\end{equation}

\textit{Repulsion} $\vec v_r(b)$, defined in Equation~\ref{eq:Repulsion1}, is the
directional movement required to prevent agents colliding. $\mathcal R_b$ is
the set of agents that are within an agent's $b$ repulsion range.

\begin{equation}\label{eq:Repulsion1}
\vec v_r(b) = 
\frac{1}{\card{\mathcal R_b}}
\left(
	\mathlarger{\mathlarger{\sum_{\vec b' \in \mathcal R_b}}}
	{\left( 1-\frac{\magn{\vec b'}}{R_b} \right)}
	\vec b'
\right)
\end{equation}
\fbox{Shouldn't this be $-\vec b'$?}

\textit{Cohesion} $\vec v_{c}(b)$, defined in Equation~\ref{eq:FlyToCentre1},
calculates the movement that makes an agent move towards other agents to form
a cohesive structure. $\mathcal C_b$ is the set of agents that are within an agent's ($b$) cohesion range.

\begin{equation}\label{eq:FlyToCentre1}
	\vec v_c(b) =
	\frac{1}{\card{\mathcal C_b}}\left({\mathlarger{\sum_{\vec b' \in
	\mathcal C_b}}{\vec b'}}\right)
\end{equation}

\textit{Direction} $\vec v_d(b)$, defined in Equation~\ref{eq:Direction},
generates a directional vector for an agent to move towards a destination
defined as $\vec d$.

\begin{equation}
\label{eq:Direction}
\vec v_d(b) = \vec d
\end{equation}

@@

Equation~\ref{eq:Obstacle2} shows the repulsion vector $\vec v_o(b)$ for an agent.
$\mathcal O_b$ is the set of obstacles that are within the range of agent $b$.
The obstacles are identified using the distance between an agent and an
obstacle $o_r$ and comparing the result to the fixed obstacle repulsion
field~$O_b$, so $\forall \vec o \in \mathcal O_b : \magn{\vec o}\leq O_b$.
The applied repulsion is calculated by scaling the normalised sum of the
normalised vectors $\hat o$ by $O_b$.  Note that $\string^$ is the equivalent
of $\hat v = \frac{\vec v}{\magn{\vec v}}$ the normalised vector.

% \begin{equation}\label{eq:Obstacle2}
% v_o(b) =
%  O_b\Bigg(\mathlarger{\mathlarger{\mathlarger{\sum}}}_{o \in O~:~\magn{ob} <= O_b}(ob)\string^\Bigg)\string^
% \end{equation}

\begin{eqnarray}\label{eq:Obstacle2}
  \vec v_o(b) & = & O_b \hat q_o \\
	\mathrm{where~}  \vec q_o & = & \sum_{\vec o\in \mathcal O_b } \hat o
	\nonumber \\
	\vec v_o(b) & = & O_b \widehat{\sum_{\vec o\in \mathcal O_b }} \hat o \nonumber
\end{eqnarray}

An agent's \textit{movement vector} is the sum of all the component vectors as
shown in Equation~\ref{eq:BotPhysics1}. This is a similar technique as used by
Hashimoto et. al.~\cite{HAY:08}. For a vector to be used for movement it be
normalised before the agent's speed ($s_b$)  can be applied. The resultant
\textit{movement vector} $\vec m_b$, as defined in Equation~\ref{eq:AgentMovement}, is calculated using unit time, speed and the normalised \textit{movement vector}.

\begin{equation}\label{eq:AgentMovement}
\vec m_b = s_b  \hat v(b)  t
\end{equation}

@@

The set of neighbours $\mathcal N_b$ (eqn \ref{set:Nb}) is sorted into a
sequence $\mathcal P_a$ with the bearing values
increasing
\begin{equation}
	\mathcal P_a = \langle (r_0,\beta_0),\ldots,(r_n,\beta_n) \rangle
\end{equation}
such that $\forall i \in \{0\ldots n-1\}: \beta_i<\beta_{i+1}$

@@

To implement void reduction full perimeter detection is required. The identification of candidate agents is incorporated into the perimeter detection algorithm as shown in Fig.~\ref{algo:checkVisibility2}. The addition is to set a status flag to highlight when a gap is detected and to record the agent's that create the gap. Concave reduction does not require the perimeter type to be identified and no communications infrastructure is required. Many coordination algorithms require inter-agent communications~\cite{MD:09,NIM:09,SOM:12,ZFG:13,JG:13}. The disadvantage of requiring a communications infrastructure is that the size of a swarm is limited through message propagation.

@@

The mid-point $\vec D(b)$ is then calculated as below in Equation~\ref{eq:ConcaveVoidPhysics3}.

\begin{equation}
\label{eq:ConcaveVoidPhysics3}
\vec D(b) = \frac{1}{2}\sum_{\vec b' \in \mathcal G_b}\vec b' 
\end{equation}

$\vec D(b)$~is the \textit{concave reduction} vector is derived from the identified
mid-point of the neighbour gap~($\mathcal{G}_b$) to the parent agent~($b$) as
shown in Equation~\ref{eq:ConcaveVoidPhysics3}.

%%\begin{equation}\label{eq:ConcaveVoidPhysics3a}
%%D(b) = bD_{pos}(b) 
%%\end{equation}
%%\fbox{\textit{do we mean product of $b$ and $D_{pos}$?}}

The final vector needs to accommodate an agent's surroundings. Due to agent
proximity it can be assumed that there are no agents in the path between the
agent and the gap, however, there may be an obstacle in the agent's path. The
\textit{concave-reduction-vector} must include an obstacle avoidance
component~$\vec v_o(b)$.  As with all the previous vector based calculations a 
weighting is applied $k_{cr}$ to allow the model to vary the intensity of the effects.  
The resultant vector $\vec V(b)$ as shown
in~Equation~\ref{eq:ConcaveVoidPhysics4}  is normalised to produce the \textit{unit-movement-vector}
$\hat V(b)$.

\begin{equation}\label{eq:ConcaveVoidPhysics4}
\vec V(b) = (k_{cr}\vec D(b) + k_o\vec v_o(b))
\end{equation}

>>>>

\documentclass{ieeeaccess}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
%\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{relsize}
\usepackage{algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\usepackage{array}
%\usepackage{caption}
%\usepackage[caption=false,font=footnotesize]{subfig}
%\usepackage{fixltx2e}
\usepackage{float}
\usepackage{url}
%\usepackage{becs}
\usepackage{listings}
\lstset{%
  basicstyle=\normalsize,
  numbers=left,
  numberstyle=\normalsize,
  stepnumber=1,
  xleftmargin=2em
}
%\usepackage{color}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\interdisplaylinepenalty=2500
\newtheorem{definition}{Definition}
\newtheorem{exampleb}{Example}
\newcommand{\subsubsubsection}[1]{\medskip\par\textit{#1:}}
\newcommand{\card}[1]{\vert{#1}\vert}
\newcommand{\magn}[1]{\vert{#1}\vert}
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{xcolor}
\usepackage{standalone}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt){figures/stableswarm} {Agent field effects.\label{methods:FieldEffects}}

@@

\begin{equation}
\mathcal N_b = \{ (r,\beta) \ldots \}
\label{set:Nb}
\end{equation}
These range and bearing pairs are the relative position vector for each
neighbour $b'$ with respect to the sensor reference frame of agent $b$.
Alternative notations are given in equation \ref{notation}
\begin{equation}
	\mathcal N_b = \{(r,\beta) \ldots \} = \{ (r_{b'}, \beta_{b'}) \ldots \} = \{
	b' \ldots \}
	\label{notation}
\end{equation}

The model use is the same as that defined by Eliot et. al. in their paper that introduces a new magnitude based metric~\cite{EKB:18}. 
Equation~\ref{eq:BotPhysics1} defines a weighted model that includes cohesion,
repulsion, direction and obstacle avoidance ($v_c(b), v_r(b),
v_d(b), v_o(b)$). 
The weightings $k_c, k_r, k_d, k_o$ allow each component to be scaled to tailor the swarming effect.

\begin{equation}\label{eq:BotPhysics1}
  v(b) = k_cv_c(b) + k_rv_r(b) + k_dv_d(b) + k_ov_o(b)
\end{equation}

\textit{Repulsion} $v_r(b)$, defined in Equation~\ref{eq:Repulsion1}, is the
directional movement required to prevent agents colliding. $\mathcal R_b$ is
the set of agents that are within an agent's $b$ repulsion range.

\begin{equation}\label{eq:Repulsion1}
v_r(b) = 
\frac{1}{\card{\mathcal R_b}}
\left(
	\mathlarger{\mathlarger{\sum_{b' \in \mathcal R_b}}}
	{\left( 1-\frac{\magn{b'}}{R_b} \right)}
	b'
\right)
\end{equation}

\textit{Cohesion} $v_{c}(b)$, defined in Equation~\ref{eq:FlyToCentre1},
calculates the movement that makes an agent move towards other agents to form
a cohesive structure. $\mathcal C_b$ is the set of agents that are within an agent's ($b$) cohesion range.

\begin{equation}\label{eq:FlyToCentre1}
	v_c(b) =
	\frac{-1}{\card{\mathcal C_b}}\left({\mathlarger{\sum_{b' \in
	\mathcal C_b}}{b'}}\right)
\end{equation}

\textit{Direction} $v_d(b)$, defined in Equation~\ref{eq:Direction},
generates a directional vector for an agent to move towards a destination
defined as $d$.

\begin{equation}
\label{eq:Direction}
v_d(b) = d
\end{equation}

@@

Equation~\ref{eq:Obstacle2} shows the repulsion vector $v_o(b)$ for an agent.
$\mathcal O_b$ is the set of obstacles that are within the range of agent $b$.
The obstacles are identified using the distance between an agent and an
obstacle $o_r$ and comparing the result to the fixed obstacle repulsion
field~$O_b$, so $\forall o \in \mathcal O_b : \magn{o}\leq O_b$.
The applied repulsion is calculated by scaling the normalised sum of the
normalised vectors $\hat o$ by $O_b$.  Note that $\string^$ is the equivalent
of $\hat v = \frac{v}{\magn{v}}$ the normalised vector.

\begin{eqnarray}\label{eq:Obstacle2}
  v_o(b) & = & O_b \hat q_o \\
	\mathrm{where~}  q_o & = & \sum_{o\in \mathcal O_b } \hat o
	\nonumber \\
	v_o(b) & = & O_b \left(\sum_{o\in \mathcal O_b }\hat o\right)^{\!\!\wedge} \nonumber
\end{eqnarray}

An agent's \textit{movement vector} is the sum of all the component vectors as
shown in Equation~\ref{eq:BotPhysics1}. This is a similar technique as used by
Hashimoto et. al.~\cite{HAY:08}. For a vector to be used for movement it be
normalised before the agent's speed ($s_b$)  can be applied. The resultant
\textit{movement vector} $m_b$, as defined in Equation~\ref{eq:AgentMovement}, is calculated using unit time, speed and the normalised \textit{movement vector}.

\begin{equation}\label{eq:AgentMovement}
m_b = s_b  \hat v(b)  t
\end{equation}

@@

The set of neighbours $\mathcal N_b$ (eqn \ref{set:Nb}) is sorted into a
sequence $\mathcal P_a$ with the bearing values
increasing
\begin{equation}
	\mathcal P_a = \langle (r_0,\beta_0),\ldots,(r_n,\beta_n) \rangle
\end{equation}
such that $\beta_0 < \beta_1 < \ldots < \beta_n$

@@

To implement void reduction full perimeter detection is required. The
identification of candidate agents is incorporated into the perimeter
detection algorithm as shown in equation~\ref{concave-predicate}. The addition is to set a status flag to highlight when a gap is detected and to record the agent's that create the gap. Concave reduction does not require the perimeter type to be identified and no communications infrastructure is required. Many coordination algorithms require inter-agent communications~\cite{MD:09,NIM:09,SOM:12,ZFG:13,JG:13}. The disadvantage of requiring a communications infrastructure is that the size of a swarm is limited through message propagation.

@@

The mid-point $D(b)$ is then calculated as below in Equation~\ref{eq:ConcaveVoidPhysics3}.

\begin{equation}
\label{eq:ConcaveVoidPhysics3}
D(b) = \frac{1}{2}\sum_{b' \in \mathcal G_b}b' 
\end{equation}

$D(b)$~is the \textit{concave reduction} vector is derived from the identified
mid-point of the neighbour gap~($\mathcal{G}_b$) to the parent agent~($b$) as
shown in Equation~\ref{eq:ConcaveVoidPhysics3}.

The final vector needs to accommodate an agent's surroundings. Due to agent
proximity it can be assumed that there are no agents in the path between the
agent and the gap, however, there may be an obstacle in the agent's path. The
\textit{concave-reduction-vector} must include an obstacle avoidance
component~$v_o(b)$.  As with all the previous vector based calculations a 
weighting is applied $k_{cr}$ to allow the model to vary the intensity of the effects.  
The resultant vector $V(b)$ as shown
in~Equation~\ref{eq:ConcaveVoidPhysics4}  is normalised to produce the \textit{unit-movement-vector}
$\hat V(b)$.

\begin{equation}\label{eq:ConcaveVoidPhysics4}
V(b) = (k_{cr}D(b) + k_ov_o(b))
\end{equation}
